Alternative Methods for Retaining Explicit and Finding Implicit Sharing in Embedded DSLs

### 2023-02-15 paper/paper.tex
small fix in intro

In the toy example
\begin{minted}{haskell}
class Exp repr where
  variable :: String -> repr Int
  constant :: String -> repr Int
  add :: repr Int -> repr Int -> repr Int
  novel :: (repr Int,repr Int) -> (repr Int,repr Int)
\end{minted}
the function \mintinline{haskell}{novel} will exhibit this issue. Since it
returns multiple outputs via a native tuple or list, it will diverge state used
to generate the DAG that cannot be captured by Kiselyov's explicit sharing
method. We will illustrate this implementation issue in Section
\ref{limitexplicit}. In our work, this translated into the inability to process
large library functions.

>>>>

In the toy example
\begin{minted}{haskell}
class Exp repr where
  variable :: String -> repr Int
  constant :: String -> repr Int
  add :: repr Int -> repr Int -> repr Int
  novel :: (repr Int,repr Int) -> (repr Int,repr Int)
\end{minted}
the function \mintinline{haskell}{novel} will exhibit this issue. Since it
returns multiple outputs via a native tuple or list, it will cause duplication
of computation that cannot be captured by Kiselyov's explicit sharing
method. We will illustrate this implementation issue in Section
\ref{limitexplicit}. In our work, this translated into the inability to process
large library functions.
